Regime transition identification for water governance at a basin scale

### 2020-11-20 tex/main/manuscript.tex
polish the introduction

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Regime transition identification for basin's governance challenges of water use}
\label{title}
% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b, 1]{Shuai Wang}  % 王老师，通讯
\author[c, d]{Xutong Wu}  % 武旭同
\author[e]{Yongping Wei} % 尉老师
\author[a, b]{Bojie Fu}  % 傅老师

@@

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
\label{significance}
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	It is a well-known fact that development of human societies backs on water use.
	Therefore, as natural water cycle has been dominated by growing socio-economic processes, big river basins are roundly governed stage by stage for further water use. 
	We propose a new method with an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
	Since our index integrates various considerations of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainable developing trajectories. 
}

@@

%tag 摘要
% 为了
\begin{abstract}
	\label{abstract}
	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
	Since water governance regime decides who gets what water, when and how much, identification for its changes is critical to guiding efficient and sustainable water uses.
	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
	Here, considering three main dimensions of water governance (storage, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
	By applying this index to the Yellow River Basin, China, it suggests there were two regimes shifts of water governance throughout half a century, which were caused by environmental, economic social and political changes.
	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
	Based on these, we summarized a widespread regime transition schema, corresponding with trajectories of water uses towards hydro-social cycle.
	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
	Since different governance challenges mainly occurred at different stages in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
\end{abstract}

@@

\label{introduction-section-1}
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for Earth system processes, but also supporting development of human societies. 
%* add references
% 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle, stage by stage
\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% 面对人类世世的重大转变，世界许多大河流域，也是经济和文明的热点地区，迫切需要成功的治理以实现可持续发展
Facing this major transformation in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for sustainable water use
\cite{bestAnthropogenicStressesWorld2019}. 
% 作为地球系统治理框架的一个组成部分，水治理需要对人类社会和水资源利用之间的复杂关系有深刻的理解。
As an integral part of a proposed Earth system governance framework, water governance requires deep understanding of the complex relationships between human societies and water use.
% Biermann et al., 2012.
% 因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scales.

\label{introduction-section-2}
% 缺乏治理就是缺乏可持续性
On the trajectory of development, missing governance means missing sustainability.
% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
According to United Nations Development Programme (UNDP), three key dimensions of water use are decided by a water governance regime directly: ``How much water can be used? (storage)'', ``How to balances different water use services? (provision)'' and ``How to allocate water equally and efficiently? (allocation)''.
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 因此，确定关于水治理的制度变化是重要的，它标志着水资源利用的实质性变化，并导致可持续性方面的新的治理挑战。
Identification of regime shifts regarding water governance, therefore, is important as a signal of substantive change in water use and lead to new governance challenges in sustainability.
% 随着环境、经济、社会和政策情况。
Changed with environmental, economic, social and political situation, the three dimensions may compose various water governance regimes. 
% 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
Firstly, effected by environment deteriorate and demands of further economic development, maintaining storage for societies can face stress because of water scarcity, but governance policies (such as construction of reservoirs for storage) are helpful to relief
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
Secondly, there is trade-off between provisioning water use (such as domestic use and food production uses) and non-provisioning water (such as uses for industrial production or energy), which in need of considerations through water governance
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
Thirdly, since allocation is a concern of the whole basin, it not only influenced by regional environmental foundations, but also changed by regions' economic comparative advantages, which is easily changed by social development and policies.
% 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes determined by three changing dimensions (storage, provision and allocation), and it is crucial to identify their shifts in a simple but comprehensive way for basins' sustainability (Figure~\ref{fig:framework}).

\label{introduction-section-3}
% 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
The Yellow River Basin (YRB, see \textit{Appendix} Methods S1 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges to water governance since ancient times.
% 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
Half century ago, the huge sediment loads of the Yellow River in China not only brought disasters, but also made it difficult for water use. 
% 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
Since 1960s, with implementations of conservation policies, regulation reservoirs, and levees constructions, these issues were effectively contained.
% 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
However, serious drying up of the Yellow River led new challenges to governance and promoted a range of related policies to deal with.
% 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
% 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
All in all, the transformation of the YRB has been the most rapid in the world in responses to the endless governance challenges induced by environmental, economic, social or political factors.
% 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
Therefore, identifying the regime shifts with challenges regarding water governance for YRB can provide insights for the world's fast-changing big river basins in their sustainable development.

\label{introduction-section-3}
% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, by integrating three above mentioned key dimensions of water governance, we develop an Integrated Water Governance Index (IWGI) at a basin scale to indicate changes of basin's water governance (Figure~\ref{fig:framework}).
% 使用案例研究
Then, by applying this index to the YRB, we analysed the regimes shifts of water governance and their main causes, in this typical basin of rapidly changes.
% 最后总结出一般性框架
Finally, we summarized a general regime transition schema, echoing to the different challenges in water governance, which can be a useful guideline for basins to develop in a coordinated way.

>>>>

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Regime transition identification for water governance at a basin scale}
\label{title}
% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
% 作者列表
\author[a, b]{Shuang Song}  % 宋爽，一作
\author[a, b]{Shuai Wang}  % 王老师，通讯
\author[c, d]{Xutong Wu}  % 武旭同
\author[e]{Yongping Wei} % 尉老师
\author[a, b, 1]{Bojie Fu}  % 傅老师

@@

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
\label{significance}
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	It is a well-known fact that development of human societies backs on water use.
	Therefore, as natural water cycle has been dominated by growing socio-economic processes, big river basins are roundly governed stage by stage for further water use. 
	We propose a new method with an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
	Since our index integrates various dimensions of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainability. 
}

@@

%tag 摘要
% 为了
\begin{abstract}
	\label{abstract}
	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
	Since water governance regime decides who gets what water, when and how much, identification for its changes is critical to guiding efficient and sustainable water uses.
	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
	Here, combining three main dimensions of water governance (storage, provision and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
	By applying this index to a typical fast-changing basin -the Yellow River Basin, China, it paints shifts between three water governance regimes throughout half a century, which were caused by environmental, economic social and political changes.
	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
	Based on these, we summarized a widespread transition schema of water governance regime, paralleled with the transformative trajectory towards hydro-social water cycle.
	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
	Since different governance challenges mainly occurred at different stages in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
\end{abstract}

@@

\label{introduction-section-1}
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for Earth system processes, but also supporting development of human societies. 
%* add references
% 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% 面对人类世世的重大转变，世界许多大河流域，也是经济和文明的热点地区，迫切需要成功的治理以实现可持续发展
Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for Sustainability
\cite{bestAnthropogenicStressesWorld2019}. 
% 作为地球系统治理框架的一个组成部分，水治理需要对人类社会和水资源利用之间的复杂关系有深刻的理解。
As an integral part of a proposed Earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
% Biermann et al., 2012.
% 因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.

\label{introduction-section-2}
% 缺乏治理就是缺乏可持续性
Missing governance means missing sustainability.
% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly (see \textit{SI Appendix} Methods S1): ``How much water can be used? (storage)'', ``How to balances different water use services? (provision)'' and ``How to allocate water equally and efficiently? (allocation)''.
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 因此，确定关于水治理的制度变化是重要的，它标志着水资源利用的实质性变化，并导致可持续性方面的新的治理挑战。
Identification of regime shifts regarding water governance, therefore, is important as a signal of substantive change in water use and lead to new challenges to sustainability.
% 随着环境、经济、社会和政策情况。
Along with environmental, economic, social and political changes, the three dimensions may compose various water governance regimes. 
% 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water storage for societies can face stress because of scarcity, but governance policies (such as construction of reservoirs) can be helpful
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
Secondly, there is trade-off between provisioning water use (such as domestic use and food production uses) and non-provisioning water (such as uses for industrial production or energy), which in need of considerations through water governance
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes.
% 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (storage, provision and allocation), and the lack of simple but comprehensive ways to identify regime shifts leaves crucial gaps towards successful governance (Figure~\ref{fig:framework}).

\label{introduction-section-3}
% 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges to water governance since the ancient time.
% 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use. 
% 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained.
% 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
However, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies to deal with.
% 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
% 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
All in all, the YRB has been the most rapid-changing basins in the world with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
% 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.

\label{introduction-section-3}
% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, based on three key dimensions of water governance, we develop an Integrated Water Governance Index (IWGI) to indicate changes of water governance at a basin scale (Figure~\ref{fig:framework}).
% 使用案例研究
Then, by applying it to the YRB, we analysed regimes shifts of water governance and their main causes.
% 最后总结出一般性框架
Finally, we summarized a general regime transition schema which can be a useful guideline for basins to develop in a coordinated way, with echoes to the different kinds of challenges regarding water governance.
